
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{ragged2e}

\usepackage{xcolor}
\hypersetup{colorlinks,urlcolor=blue}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\achievementItem}[1]{
  \item\small{
    {#1 \vspace{-6pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\justify \begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape rohit tiwari} \\ \vspace{1pt}
    % 123 Street Name, Town, State 12345 \\ 
    \vspace{5pt}
    % \small \raisebox{-0.1\height}\faPhone\ 9871626616 ~ 
    \raisebox{-0.2\height}\faEnvelope\ \href{mailto:knowrohit.07@gmail.com}{ knowrohit.work@gmail.com} ~ 
    \raisebox{-0.2\height}\faLinkedin\ \href{https://www.linkedin.com/in/rohit-tiwari-907387204/}{LinkedIn} ~
    \raisebox{-0.2\height}\faGithub\ \href{https://github.com/knowrohit}{Github} ~ 
    \vspace{-8pt}
\end{center}

% %-----------EDUCATION-----------
% \section{Education}
%    \resumeSubHeadingListStart
%     \resumeSubheading
%       {Amity University, Noida}{Jul '19 -- May '23}
%       {B.Tech in Computer Science Engineering}{8.5 CGPA}
%   \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {{TartanHQ}\href{https://www.tartanhq.com/}{}}{July '22 -- April '23}
      {Data Scientist}{}
      \vspace{-7pt}
      \resumeItemListStart
        \resumeItem{Successfully deployed and fine-tuned Document extraction OCR models using LayoutLM v3 on AWS EC2, replacing third party APIs with inbuilt solution}
        \resumeItem{Built and deployed models for Document Classification, Payslip Forgery, and Blur Detection using Tesseract, Torchvision, Detectron2, and Spacy NLP, achieving a 95 percent accuracy rate.}
        
        \resumeItem{Analyzed Data inflow, timestamps of Payslips, and their metadata using Apache Superset (MySQL); contributed to the development of a custom annotation tool for OCR.}
      \resumeItemListEnd

    \resumeSubheading
      {{Trill Marketplace} \href{https://trillmrkt.com/}{}}{February '21 -- March '22}
      {Machine Learning Engineer}{}
      
      \vspace{-7pt}
      \resumeItemListStart
        \resumeItem{Developed an LLM for customer assistance using GPT-NEO(20B); incorporated CI/CD pipelines for model updates and deployment.}
        \resumeItem{Worked on ML systems using Google Pegasus in production to scrape and learn from the clustered/textual data of streetwear customers.}
        \resumeItem{Collaborated with data engineering teams to establish robust data pipelines,  used MLflow for tracking experiments, reproducibility, and model versioning.}
      \resumeItemListEnd
      
    \resumeSubheading
      {{GooseAI}\href{https://goose.ai/}{}}{April '21 -- July '21}
      {Data Science: Intern}{}
      \vspace{-7pt}
      \resumeItemListStart
        \resumeItem{ Contributed on experimental ML with physics such as Phononics, and federated learning, achieving a 90 percent success rate in simulations.}
      \resumeItemListEnd
      
    
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{Saraswati LLM} $|$ \emph{Transformers, Node-js, JavaScript, Docker} $|$ \href{}{}}{} 
            \resumeItemListStart
                \resumeItem{A full-stack application allowing students to upload academic documents and engage with my own state-of-the-art LLM, "Saraswati".}
                \resumeItem{RAG System: Upload academic content (books, PDFs). Uses Sentence Transformers for embedding, FAISS indexing for similarity matching, and integrates with LLM for generating personalized answers based on chunks + query.}
                \resumeItem{Code Scripting: Generate scripts in various programming languages, trained on 20k high-quality leetcode and stackoverflow infilling samples.}
                \resumeItem{Logical / IQ Tasks: Perform arithmetic, and chain-of-thought reasoning.}
                \resumeItem{Model performance: Competing with GPT-3.5 in benchmarks and overall utility.}
          \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{know-medical-dialogues} $|$ \emph{HuggingFace,Datasets,LLM} $|$ \href{https://huggingface.co/datasets/knowrohit07/know_medical_dialogue_v2}{HuggingFace}}{}
            \resumeItemListStart
                \resumeItem{Dataset of conversational exchanges between patients and doctors on diverse medical topics, covers a wide range of medical queries and advice.}
                \resumeItem{Beneficial for healthcare professionals, especially in resource-limited regions. Facilitates AI-assisted medical roleplays on affordable devices if trained on quantized LLMs.}
                \resumeItem{Derived from anonymized patient-doctor seed interactions and then synthetically generated via GPT4.}
            \resumeItemListEnd  
        \resumeProjectHeading
                {\textbf{VirgilAbloh GPT} $|$ \emph{Transformers, PyTorch, GLM} $|$ \href{https://github.com/knowrohit/virgilablohGPT}{Github}}{} 
            \resumeItemListStart
                \resumeItem{Virgil engages in fashion-related conversations, provides tailored recommendations, and offers assistance on various tasks like coding, humour.}
                \resumeItem{Utilized transformers and decoding methods to mimic the user's talking style, also using Text-to-Speech Conversion}
                \resumeItem{Virgil’s heart lies a complex autoregressive language model GLM that utilizes deep learning to produce human-like text.}
          \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Fashion RecSys} $|$ \emph{Tensorflow, Azure, Docker, HuggingFace, BS4} $|$ \href{https://github.com/knowrohit/Fashion-Rec-Sys}{GitHub}}{} 
            \resumeItemListStart
                \resumeItem{AI-powered product recommender system designed to help users find their perfect fashion match with user-friendly UI.}
                \resumeItem{Implemented feature extraction using Cosine similarities, ResNet hidden layers, and Azure image tags.}
                \resumeItem{New updates will have video-based recommendations using GCP video intelligence, to be deployed soon.}
          \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{NFT-GAN} $|$ \emph{torchvision, Numpy, PIL, scipy} $|$ \href{https://github.com/knowrohit/NFT-GAN}{GitHub}}{} 
            \resumeItemListStart
                \resumeItem{Developed an NFT-GAN for creating NFT avatar and collectible projects using Gmapping and Gsynthesis.}
                \resumeItem{Configured image generation processes to control trait rarity and generate JSON metadata for NFTs in compliance with OpenSea metadata requirements.}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Open Source Projects} $|$ \emph{HuggingFace, Datasets, LLMs}  $|$ \href{https://huggingface.co/knowrohit07}{HuggingFace}}{}
            \resumeItemListStart
                \resumeItem{Clean uncensored datasets using Self-instruct fine tuning.}
                \resumeItem{regular updates with large majority of HF models, in any modality (text, vision, multi-modal, etc.)}
          \resumeItemListEnd
               
          

            
    \resumeSubHeadingListEnd

 
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{:Python, C/C++, SQL} \\
     \vspace{1pt}
     \textbf{Technologies}{: Anaconda, Apache, NVIDIA Cuda, Linux, Jupyter, PostgreSQL, Azure, Shopify, WordPress} \\
     \vspace{1pt}
     \textbf{Developer Tools}{: Git, Docker, Microsoft Azure ML, VS Code, AWS Sagemaker, AWS EC2} \\
     \vspace{1pt}
     \textbf{Libraries}{: PyTorch, TensorFlow, CUDA, gRPC, Langchain, chromaDB, Numpy, Pandas, Scikit-Learn, OpenCV, FastAPI, Flask} \\
     \vspace{1pt}
     \textbf{MLOPS}{: Kubeflow, MLflow, WeightsBiases} \\
    }}
 \end{itemize}



%-----------INVOLVEMENT---------------
\section{EXTRA-CURRICULAR}

\begin{itemize}[leftmargin=0.2in]

  \achievementItem{Member of Amity Linux Assistance Sapience Club(ALiAS)}
  \achievementItem{Zonal-Level Football Champion, BBFS FC}

\end{itemize}

\end{document}
